Solutions to the Assignment - 2 : CS6230 - \\ Optimization Methods in Machine Learning

### 2017-10-10 Assignment-2/Solns-Assgn-2.tex
Assgn-2 Update 3

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bookmark}

@@

Using \ref{sub-ans-1b}, we replicate the same statement from Question 1a, which is:
\begin{equation}
\label{ans-1b}
\partial f = \text{Conv}\left(\{\partial f_{i}(x) | f_{i}(x) = f(x) \text{ and } i \in \{1 \ldots m\}\}\right)
\end{equation}

where the \(\text{Conv}(S)\) in \ref{sub-ans-1b} and \ref{ans-1b} denotes the set of all convex combinations of the elements of \(S\)/convex hull of \(S\).

\end{flushleft}

@@

Using the definition of \(\textbf{prox}_{h, t}(x - t\nabla g(x)) = x - tG_{t}(x)\) in \ref{update-subgrad-optim}, we get:
\begin{equation}
\label{part-c}
x - t\nabla g(x) - x + tG_{t}(x) \in \partial h(x - tG_{t}(x)) \implies tG_{t}(x) - tg(x) \in \partial h(x - tG_{t}(x))
% @TODO: Need to check this equation
\end{equation}
\end{flushleft}

>>>>

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bookmark}
\usepackage{hyperref}

@@

Using \ref{sub-ans-1b}, we replicate the same statement from \ref{ans-1a}, which is:
\begin{equation}
\label{ans-1b}
\partial f = \text{Conv}\left(\{\partial f_{i}(x) | f_{i}(x) = f(x) \text{ and } i \in \{1 \ldots m\}\}\right)
\end{equation}

where the \(\text{Conv}(S)\) in \ref{sub-ans-1b} and \ref{ans-1b} denotes the set of all convex combinations of the elements of \(S\)/convex hull of \(S\).
\end{flushleft}

\subsection*{Part c}
\begin{flushleft}
\begin{equation}
\label{ques-1c}
\displaystyle f(x) = \sup_{0 \leq t \leq 1} x_{1} + x_{2}t + \ldots + x_{n}t^{n-1}
\end{equation}

Since the set \([0, 1]\) over which the supremum is being taken over in \ref{ques-1c} is closed and bounded, meaning it is compact, following from the lecture notes\footnote{\href{https://see.stanford.edu/materials/lsocoee364b/01-subgradients_notes.pdf}{Boyd and Vanderberghe Lecture Notes on Subgradients}}, we can apply the same intuition as done for \ref{ques-1a} and \ref{ques-1b}. In this case, it is required that \(p(t)\) is sub-differentiable w.r.t. \(x\). This is assured since the gradient is:
\begin{equation}
\label{sub-ans-1c}
\displaystyle \nabla_{x} p(t) =  \langle 1, t, \ldots, t^{n-1} \rangle
\end{equation}

Using \ref{sub-ans-1c}, we use the same statement as in \ref{ans-1a} and \ref{ans-1b},
\begin{equation}
\label{ans-1c}
\displaystyle \partial f = \text{Conv}\left(\{\nabla_{x} f(x) | f(x) = \sup p(t), t \in [0, 1]\}\right)
\end{equation}

where the \(\text{Conv}(S)\) if \ref{ans-1c} denotes the set of all convex combinations of the elements of \(S\)/convex hull of \(S\).
\end{flushleft}

\subsection*{Part d}
\begin{flushleft}
\begin{equation}
\label{ques-1d}
\displaystyle f(x) = x_{[1]} + x_{[2]} + \ldots + x_{[k]}
\end{equation}

Clearly, those indices not involved in the first \(k\) highest values will have their partial derivatives to be \(0\) and those indices involved in the first \(k\) highest values will have their partial derivatives to be \(1\). 
\(\newline\)

To get these indices, we need to maintain a copy of the vector and sort the elements of that copy. Note the indices involved in the top \(k\) values. Call the set to be \(S\). Hence the subgradient for \ref{ques-1d} would be:
\begin{equation}
\label{ans-1d}
\displaystyle g \text{ such that } g_{i} = \begin{cases} 1 & \text{ if } i \in S \\ 0 & \text{ otherwise} \end{cases}
\end{equation}

Note that \ref{ans-1d} will vary based on the value of \(k\) too. 
\end{flushleft}
\newpage

@@

Using the definition of \(\textbf{prox}_{h, t}(x - t\nabla g(x)) = x - tG_{t}(x)\) in \ref{update-subgrad-optim}, we get:
\begin{equation}
\label{sub-part-c}
x - t\nabla g(x) - x + tG_{t}(x) \in \partial h(x - tG_{t}(x)) \implies tG_{t}(x) - t\nabla g(x) \in \partial h(x - tG_{t}(x)) 
\end{equation}

Using \ref{sub-part-c}, we have:
\begin{equation}
\label{part-c}
\implies G_{t}(x) - \nabla g(x) \in \partial h(x - tG_{t}(x))
% TODO: Need to check this equation
\end{equation}
\end{flushleft}
